---
title: "ggvis overview"
output:
  ggvis:::html_document
---

<!--
%\VignetteEngine{knitr}
%\VignetteIndexEntry{ggvis basics}
-->

```{r, echo = FALSE, message = FALSE}
library(knitr)
library(ggvis)
opts_chunk$set(comment = "#>", error = FALSE, tidy = FALSE)
opts_chunk$set(fig.width = 2.5, fig.height = 1.5, dpi = 100)
```


<div class="container">
<div class="row">
<div class="col-md-5">
ggvis is a data visualization package for R which lets you:

* Declaratively describe data graphics with a syntax that is similar to ggplot2.
* View and interact with the graphics on your local computer, or use them in an interactive web application with [Shiny](http://www.rstudio.com/shiny/).

Data manipulation and transformation are done in R, and the graphics are rendered in a web browser, using [Vega](https://github.com/trifacta/vega/). For RStudio users, ggvis graphics display in a viewer panel, which is possible because RStudio is a web browser.

Presently, ggvis is in an alpha stage, and its API is still evolving.  We strongly recommend that you do not rely on this for production, but feel free to explore. For questions and other discussion, please use [mailing list](https://groups.google.com/group/ggvis).

ggvis is not yet available on CRAN, but you can install it directly from GitHub. Make sure you have the latest version of devtools (at least 1.4) and run the following:

```{r, eval = FALSE}
devtools::install_github(c("hadley/testthat", "rstudio/shiny", "rstudio/ggvis"))
```

The ggvis source code is hosted at https://github.com/rstudio/ggvis.

</div>
<div class="col-md-7">


## Getting started with ggvis

* See some [quick examples](quick-examples.html)
* Learn [ggvis basics](ggvis-basics.html)
* Read more about [interactive graphics](interactivity.html)

## More advanced topics

* How to control [axes and legends](axes-legends.html)
* How to use [properties and scales](properties-scales.html)
* Learn about [layers](layers.html)
* Plumbing: about ggvis's [data hierarchy](data-hierarchy.html)

## More about ggvis

* Differences and similarities to [ggplot2](ggplot2.html)
* The relationship between ggvis and [Vega](vega.html)

</div>
</div>
</div>

*****

## Examples of ggvis graphics

<div class="container">
<div class="row">
<div class="col-md-5">
Histogram:

```{r, results = 'asis', echo = FALSE, message = FALSE, fig.width = 3}
# Histogram
ggvis(faithful, props(x = ~eruptions, fill := "#ffffdd", fill.hover := "#eebbbb")) +
  layer_histogram() +
  guide_axis("x", title = "eruptions") +
  guide_axis("y", title = "count")
```
</div>
<div class="col-md-7">
Scatterplot with model fit line and interactive control:

<iframe id="histogram" src="https://winston.shinyapps.io/ggvis-quick-examples-smooth-span/?viewer_pane=1" style="border: none; width: 400px; height: 400px"></iframe>
</div>
</div>
</div>

